The value of intermediation

### 2022-09-15 src/presentation/presentation.qmd
Add mathjax setup to header

---
title: "The value of intermediation"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        transition: fade
        toc: true
        toc-depth: 1
        toc-title: Agenda
bibliography: references.bib
---

# Intorduction

@@

::: {.fragment .fade-in fragment-index=6}
**Idea:** 2. stage bargaining is over *final allocations*
:::
:::

>>>>

---
title: "The value of intermediation"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        html-math-method: mathjax
        transition: fade
        toc: true
        toc-depth: 1
        toc-title: Agenda
        header-includes: |
          <script>
            MathJax = {
                loader: {load: ["input/tex", "output/svg"]}
                svg: {
                  scale: 0.9
                },
                chtml: {
                  scale: 0.9
                }
            };
          </script>
bibliography: references.bib
---

# Introduction

@@

::: {.fragment .fade-in fragment-index=6}
**Idea:** stage 2 bargaining is over *final allocations*
:::
:::
